Data_Analysis_exp7

### 2017-12-24 Traditional_Analysis/Analysis_exp7_2.rmd
revise the rmarkdown file

---
title: "Analysis_exp7"
author: "hcp"
date: "2016-10-28"
output: word_document
---
<style type="text/css">

@@

pkgNeeded <- (c("tidyverse","plyr","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))

@@

```{r loadingData_e7,echo=FALSE,results='hide'}
df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
# render the numeric column
cols.num <- c("Age","Block","Bin","Trial","RT","Accuracy")
# Tcols.num <- c("SubjectID","Age","Block","Bin","Trial","RT","Accuracy")
df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)
df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)

colnames(df.L)[colnames(df.L)=="Accuracy"] <- "ACC"
colnames(df.T)[colnames(df.T)=="Accuracy"] <- "ACC"
colnames(df.L)[colnames(df.L)=="SubjectID"] <- "Subject"
colnames(df.T)[colnames(df.T)=="SubjectID"] <- "Subject"

@@

df.L$Morality[df.L$Morality == 'moral'] <- 'Good'
df.L$Morality[df.L$Morality == 'immoral'] <- 'Bad'
df.L$Identity[df.L$Identity == 'self'] <- 'Self'
df.L$Identity[df.L$Identity == 'other'] <- 'Other'

df.L$Morality <- factor(df.L$Morality, levels=c("Good","Bad")) # make the variables in a specified order
df.L$Identity <- factor(df.L$Identity, levels=c("Self","Other")) # make the variables in a specified order
df.L$Match <- factor(df.L$Match, levels=c("match","nonmatch")) # make the variables in a specified order

df.T$Morality[df.T$Morality == 'moral'] <- 'Good'
df.T$Morality[df.T$Morality == 'immoral'] <- 'Bad'
df.T$Identity[df.T$Identity == 'self'] <- 'Self'
df.T$Identity[df.T$Identity == 'other'] <- 'Other'
df.T$Task[df.T$Task == 'Self'] <- 'ID'
df.T$Task[df.T$Task == 'self'] <- 'Id_task'
df.T$Task[df.T$Task == 'moral'] <- 'Valence_task'
df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad")) # make the variables in a specified order
df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other")) # make the variables in a specified order
```

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L
df.T1 <- df.T
df.L1$RT <- df.L1$RT*1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000

@@

length(unique(df.L1.valid$Subject)) + length(excld.sub) == length(unique(df.L1$Subject))
# excld.trials3 <- excld.trials[!(excld.trials$Subject %in% excld.sub),]
excld.trials.L <- df.L1.valid[df.L1.valid$RT <= 200,]
df.L1.V <- df.L1.valid[!(df.L1.valid$RT <= 200),] 
excld.trials.T <- df.T1.valid[df.T1.valid$RT <= 200,]
df.T1.V <- df.T1.valid[!(df.T1.valid$RT <= 200),] 
nrow(excld.trials.T) + nrow(df.T1.V) == nrow(df.T1.valid) # if true, everything is ok

@@

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_L, echo=FALSE, results='hide',warning=FALSE, message=FALSE}
# calculate the d prime for each condition
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "FA"
        }
}

@@

# long format to wide
df.L1.V.SDT_w <- dcast(df.L1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0
df.L1.V.SDT_w$FA[is.na(df.L1.V.SDT_w$FA)] <- 0
df.L1.V.SDT_w$hitR <- df.L1.V.SDT_w$hit/(df.L1.V.SDT_w$hit + df.L1.V.SDT_w$miss)
df.L1.V.SDT_w$faR <- df.L1.V.SDT_w$FA/(df.L1.V.SDT_w$FA + df.L1.V.SDT_w$CR)

>>>>

---
title: "Data_Analysis_exp7"
author: "hcp"
date: "2017-12"
output: word_document
---
<style type="text/css">

@@

pkgNeeded <- (c("plyr","tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))

@@

```{r loadingData_e7,echo=FALSE,results='hide'}
df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) # data for matching task
df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)  # data for categorization task

# render the data in numeric format for future analysis
cols.num <- c("Age","Block","Bin","Trial","RT","Accuracy")
df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)  
df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)

# rename columns
colnames(df.L)[colnames(df.L)=="Accuracy"]  <- "ACC"
colnames(df.T)[colnames(df.T)=="Accuracy"]  <- "ACC"
colnames(df.L)[colnames(df.L)=="SubjectID"] <- "Subject"
colnames(df.T)[colnames(df.T)=="SubjectID"] <- "Subject"

@@

# Change the name for different levels of independent variables
df.L$Morality[df.L$Morality == 'moral']   <- 'Good'
df.L$Morality[df.L$Morality == 'immoral'] <- 'Bad'
df.L$Identity[df.L$Identity == 'self']    <- 'Self'
df.L$Identity[df.L$Identity == 'other']   <- 'Other'

# make the variables in a specified order
df.L$Morality <- factor(df.L$Morality, levels = c("Good","Bad"))    
df.L$Identity <- factor(df.L$Identity, levels = c("Self","Other"))  
df.L$Match    <- factor(df.L$Match,    levels = c("match","nonmatch"))

# Change the name for different levels of independent variables
df.T$Morality[df.T$Morality == 'moral']   <- 'Good'
df.T$Morality[df.T$Morality == 'immoral'] <- 'Bad'
df.T$Identity[df.T$Identity == 'self']    <- 'Self'
df.T$Identity[df.T$Identity == 'other']   <- 'Other'
df.T$Task[df.T$Task == 'Self']            <- 'ID'
df.T$Task[df.T$Task == 'self']            <- 'Id_task'
df.T$Task[df.T$Task == 'moral']           <- 'Valence_task'

# make the variables in a specified order
df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad"))    
df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))
```

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L
df.T1 <- df.T
df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000

@@

# check the number of participants are correct
length(unique(df.L1.valid$Subject)) + length(excld.sub) == length(unique(df.L1$Subject))
# excld.trials3 <- excld.trials[!(excld.trials$Subject %in% excld.sub),]
excld.trials.L <- df.L1.valid[df.L1.valid$RT <= 200,]
df.L1.V        <- df.L1.valid[!(df.L1.valid$RT <= 200),]  # valid trial data for match task
excld.trials.T <- df.T1.valid[df.T1.valid$RT <= 200,]
df.T1.V        <- df.T1.valid[!(df.T1.valid$RT <= 200),]  # valid trial data for categorization task
nrow(excld.trials.T) + nrow(df.T1.V) == nrow(df.T1.valid) # if true, everything is ok

@@

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_L, echo=FALSE, results='hide',warning=FALSE, message=FALSE}
## calculate the d prime for each condition
# calculate the number of hit,CR,miss or FA 
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "FA"
        }
}

@@

# long format to wide
df.L1.V.SDT_w <- dcast(df.L1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0 # transfer NA to 0
df.L1.V.SDT_w$FA[is.na(df.L1.V.SDT_w$FA)]     <- 0
df.L1.V.SDT_w$hitR <- df.L1.V.SDT_w$hit/(df.L1.V.SDT_w$hit + df.L1.V.SDT_w$miss)
df.L1.V.SDT_w$faR <- df.L1.V.SDT_w$FA/(df.L1.V.SDT_w$FA + df.L1.V.SDT_w$CR)
